---
title: "An analysis on the next genetation on home consoles "
author: "10392665, 10684078, 10557474"
output: beamer_presentation

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(rtweet)
library(ggplot2)
library(dplyr)
library(ggthemes)
library(readr)
library(jsonlite)
library(tidytext)
library(wordcloud)
library(wordcloud2)
library(tidyr)
library(maps)
library(graphics)

setwd("C://Users//ELISW//Documents//UNI//Data")

playstation_english <-  read_csv("playstation_tweets_english.csv", col_names = TRUE)
xbox_x_english <-  read_csv("xboxseriesx_tweets_english.csv", col_names = TRUE)
```



## Introduction

TITLE NAMES ARE TEMP

Please place the introduction here

## Another slide left for introductions 

## Our Aims: 

- Which console is more discussed, Xbox or PlayStation?
- Which console do people prefer?
- What is the most important factor when people choose which to buy? 
- What are the strategies that each console use in the market?
- Which kind of games are more preferable?
- Which game is the most popular?

## Sentiment analysis for xbox and PlayStation (inc. t-test)


## Retweets contrast (graph) + disscuss sentiment correlation  

## Sentiment over time

## Tweet Count from offical Xbox and Playstation Twitter

```{r, echo = FALSE}
  
ps <- as.Date(as.POSIXct(playstation_english$created_at,format='%Y%M%D'))
xb <- as.Date(as.POSIXct(xbox_x_english$created_at,format='%Y%M%D'))

playstation_english <- cbind(playstation_english,ps)
xbox_x_english <- cbind(xbox_x_english,xb)

ctx <- playstation_english %>% group_by(ps) %>% count()

ctp <- xbox_x_english %>% group_by(xb) %>% count()

## Cont
ggplot() + 
  geom_area(data = ctp,aes(x = xb, y = n, color = "#E7B800", fill = "#E7B800"), 
            alpha = 0.5, position = position_dodge(0.8)) +
  geom_area(data = ctx,aes(x = ps, y = n,color = "#00AFBB", fill = "#00AFBB"), 
            alpha = 0.5, position = position_dodge(0.8)) +
  labs(x = NULL, y = NULL,title = "Frequency of Tweets From #Xbox and #Playstation",
       subtitle = "Twitter status (tweet) counts aggregated using 1-days intervals",
       caption = "Source: Data collected from Twitter's REST API via rtweet")+
  scale_color_manual(values = c("#00AFBB", "#E7B800")) +
  scale_fill_manual(values = c("#00AFBB", "#E7B800"),
                    name  ="Console",
                    labels=c("Playstation", "Xbox")) +
  guides(color=FALSE) 
```


## Locations of each tweet

## Wordclouds

## Bar chart tweets volume of price X Hardware

## Barchart of most disscussed games

## Sentiment for top 10 most discussed

## Which platform are the most positives sentiments on

## Genre barplots (find gap in the market)

## Conclusion 

## Limitations



